Machine Learning for Real-Time, Automatic, and Early Diagnosis of Parkinson’s Disease by Extracting Signs of Micrographia from Handwriting Images

### 2021-11-24 Submission/Paper/Paper.tex
uploading paper to arXiv

 % use the "wcp" class option for workshop and conference
 % proceedings
 %\documentclass[gray]{jmlr} % test grayscale version
 %\documentclass[tablecaption=bottom]{jmlr}% journal article
 \documentclass[pmlr,twocolumn,10pt]{jmlr} % W&CP article

@@

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{url}
\usepackage{breakurl}
\usepackage[breaklinks]{hyperref}
\def\UrlBreaks{\do\/\do-}

@@

\usepackage[table]{xcolor}
\newcommand\red[1]{{\color{red}#1}}

@@

 % change the arguments, as appropriate, in the following:
\jmlrvolume{LEAVE UNSET}
\jmlryear{2021}
\jmlrsubmitted{LEAVE UNSET}
\jmlrpublished{LEAVE UNSET}
\jmlrworkshop{Machine Learning for Health (ML4H) 2021} % W&CP title

@@

% Authors with different addresses and equal first authors:
% \author{Riya Tyagi \nametag{\thanks{Authors contributed equally}},
% Tanish Tyagi \nametag{\footnotemark[1]}, 
% Ming Wang,
% Lijun Zhang
% \centering \Email{ 
% \\[\bigskipamount]  
% rtyagi@exeter.edu, ttyagi@mgh.harvard.edu, mwang@phs.psu.edu, lzhang6@pennstathealth.psu.edu}
% }

@@

    \subfloat{{\includegraphics[scale = 0.55]{images/logreg_roc.png} }}%
    \subfloat{\includegraphics[scale = 0.55]{images/svm_roc.png}} %

\end{figure*}

\section{Methods}
\label{Methodology}

@@

\section{Conclusion and Future Works}
\label{Conclusion+FutureWorks} 
In this work, we applied classification algorithms to handwriting samples to diagnose Parkinson's disease in its early stages. Our dataset was relatively small in size, which we will address in the future by gathering data through our web portal. Our mockups and plans for the website are detailed in Appendix \ref{app:webportal}.  Additionally, we devised a handwriting assessment based on precedents and open-source datasets in this research area, which is available in Appendix \ref{app:assessment}. Once the web portal is complete, we hope to perform clinical studies with our partners from Penn State University. In these studies, we will evaluate the handwriting assessment and develop a handwriting dataset that considers temporal stages of Parkinson’s disease by analyzing handwriting and drawing samples from different stages of PD.

After completing the web portal, we hope to boost the accessibility of our handwriting assessment through online deployment. Ideally, a patient with a touch-screen device, such as a phone or tablet, will be able to take a quick, easy, online assessment. This also enables us to take advantage of device signals. A similar exercise, with typing instead of drawing, can be performed using keystroke data from a computer.

@@

\bibliography{jmlr-sample}
\UrlBreaks
\nocite{*}
\justifying

@@

\vfill\null
\columnbreak

>>>>

 % use the "wcp" class option for workshop and conference
 % proceedings
 %\documentclass[gray]{jmlr} % test grayscale version
 %\documentclass[tablecaption=bottom]{jmlr}% journal article
 \documentclass[pmlr,twocolumn,10pt,breaklinks, x11names,table]{jmlr} % W&CP article

@@

 % The booktabs package is used by this sample document
 % (it provides \toprule, \midrule and \bottomrule).
 % Remove the next line if you don't require it.
\usepackage{url}
\usepackage{breakurl}
\usepackage{ragged2e}
% \usepackage[breaklinks]{hyperref}
\def\UrlBreaks{\do\/\do-}

@@

% \usepackage[table]{xcolor}
\newcommand\red[1]{{\color{red}#1}}

@@

 % change the arguments, as appropriate, in the following:
\jmlrvolume{ML4H Extended Abstract Arxiv Index}
\jmlryear{2021}
\jmlrsubmitted{2021}
\jmlrpublished{}
\jmlrworkshop{Machine Learning for Health (ML4H) 2021} % W&CP title

@@

% Authors with different addresses and equal first authors:
\author{Riya Tyagi \nametag{\thanks{Authors contributed equally}},
Tanish Tyagi \nametag{\footnotemark[1]}, 
Ming Wang,
Lijun Zhang
\centering \Email{ 
\\[\bigskipamount]  
rtyagi@exeter.edu, ttyagi@mgh.harvard.edu, mwang@phs.psu.edu, lzhang6@pennstathealth.psu.edu}
}

@@

    {{\includegraphics[scale = 0.55]{images/logreg_roc.png} }}%
    {\includegraphics[scale = 0.55]{images/svm_roc.png}} %

\end{figure*}
\section{Methods}
\label{Methodology}

@@

\section{Conclusion and Future Works}
\label{Conclusion+FutureWorks} 
In this work, we applied classification algorithms to handwriting samples to diagnose Parkinson's disease in its early stages. Our dataset was relatively small in size, which we will address in the future by gathering data through our web portal. Our mockups and plans for the website are detailed in Appendix \ref{app:webportal}.  Additionally, we devised a handwriting assessment based on precedents and open-source datasets in this research area, which is available in Appendix \ref{app:assessment}. We strive to boost the accessibility of our handwriting assessment by online deployment through a web portal. Ideally, a patient with a touch-screen device will be able to take a quick, easy, online assessment. Once the web portal is complete, we hope to perform clinical studies with our partners from Penn State University. In these studies, we will evaluate the handwriting assessment and develop a handwriting dataset that considers temporal stages of Parkinson’s disease by analyzing handwriting and drawing samples from different stages of PD.

@@

\bibliography{jmlr-sample}
%\UrlBreaks
\nocite{*}
\justify{}

@@

\vfill\eject
% \columnbreak
